Supplementary Figures

### 2024-09-04 supplementary_plots.Rmd
updates for review

cowplot::plot_grid(A, B, nrow = 2, rel_heights = c(1.5, 1), align = 'v', axis = 'lr', labels = 'auto') |> 
  ggsave(filename = './Plots/FigureS4.png', width = 19, height = 16, units = 'cm')
```
```{r}
skill_summary_RW <- temperature_skill_RW |>
  group_by(model_id) |>
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |>
  ungroup() |>
  filter(mean_crps < 0) |>
  left_join(model_meta) |>
  mutate(manuscript_name = fct_reorder(manuscript_name, mean_crps),
         uses_NOAA = ifelse(uses_NOAA == 1, 'yes', 'no'),
         uses_AT = str_detect(NOAA_var, 'air_temperature')) |>
  ggplot(aes(x=mean_crps, y = manuscript_name, fill = model_type)) +    # Different pattern for each group
  geom_bar_pattern(aes(pattern = as.factor(uses_AT)),
                   stat = "identity",
                   alpha = 0.8,
                   pattern_fill = "black",
                   pattern_colour = "black",
                   pattern_spacing = 0.04,
                   pattern_alpha = 1,
                   colour = 'black') +
  scale_y_reordered() +
  labs(y='Model', x = 'Mean relative skill (°C)') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe')) +
  scale_pattern_type_manual(values=c(NA, NA)) +
  theme_bw(base_size = 10) +
  guides(pattern = guide_legend(override.aes = list(fill = "white", pattern_spacing = 0.02),
                                title = 'Uses air temperature\nas a covariate?'),
         fill = guide_legend(override.aes = list(pattern = "none"), title = 'Model class')) +
    theme(legend.box = 'horizontal')

@@

ggpubr::ggarrange(ggarrange(NULL, as_ggplot(get_legend(skill_summary_RW)), NULL, NULL, widths =  c(0.2, 0.9,0.2, 1.1), nrow = 1),
                  ggarrange(skill_summary_RW_nolegend,  NULL, skill_horizon_RW, align = 'h', widths =  c(0.9,0.05, 1.1), nrow = 1), 
                  heights = c(0.5, 1),nrow = 2) |> 
  ggsave(filename = 'Plots/FigureSnew.png', height = 17, width = 18, units = 'cm')
```
```{r}
null_scores <- temperature_scores |> mutate(horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) %>% 
  filter(model_id %in% baselines$model_id, 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |> 
  group_by(model_id, horizon) |> 
  summarise(mean_crps = mean(crps, na.rm = T)) %>% 
  mutate(model_id = factor(model_id, levels = c('climatology', 'persistenceRW'), labels = c("day-of-year", "persistence"))) %>% 
  ggplot(aes(x=horizon,y = mean_crps, colour = model_id)) + 
  geom_line() + 
  scale_x_continuous(breaks = seq(2,30, 2)) + 
  theme_bw() + 
  labs(x= 'Horizon (days)', y = 'Mean CRPS (°C)') + 
  scale_colour_viridis_d(name = 'Null Model', begin = 0.2, end=0.9) +
  theme(panel.grid.minor = element_blank())

ggsave(null_scores, filename = 'Plots/Figure_Snew2.png', height = 10, width = 15, units = 'cm')
```

>>>>

cowplot::plot_grid(A, B, nrow = 2, rel_heights = c(1.5, 1), align = 'v', axis = 'lr', labels = 'auto') |> 
  ggsave(filename = './Plots/FigureS4.png', width = 19, height = 16, units = 'cm')
```
```{r}
temp_skill_RW <- temperature_skill_RW |>
  group_by(model_id) |>
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |>
  ungroup() |>
  filter(mean_crps < 0) |>
  left_join(model_meta) |>
  mutate(manuscript_name = fct_reorder(manuscript_name, mean_crps),
         uses_NOAA = ifelse(uses_NOAA == 1, 'yes', 'no'),
         uses_AT = str_detect(NOAA_var, 'air_temperature')) |>
  ggplot(aes(x=mean_crps, y = manuscript_name, fill = model_type)) +    # Different pattern for each group
  geom_bar_pattern(aes(pattern = as.factor(uses_AT)),
                   stat = "identity",
                   alpha = 0.8,
                   pattern_fill = "black",
                   pattern_colour = "black",
                   pattern_spacing = 0.04,
                   pattern_alpha = 1,
                   colour = 'black') +
  scale_y_reordered() +
  labs(y='Model', x = 'Mean relative skill (°C)') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe')) +
  scale_pattern_type_manual(values=c(NA, NA)) +
  theme_bw(base_size = 10) +
  guides(pattern = guide_legend(override.aes = list(fill = "white", pattern_spacing = 0.02),
                                title = 'Uses air temperature\nas a covariate?'),
         fill = guide_legend(override.aes = list(pattern = "none"), title = 'Model class')) +
    theme(legend.box = 'horizontal')

DO_skill_RW <- oxygen_skill_RW |>
  group_by(model_id) |>
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |>
  ungroup() |>
  filter(mean_crps < 0) |>
  left_join(model_meta) |>
  mutate(manuscript_name = fct_reorder(manuscript_name, mean_crps),
         uses_NOAA = ifelse(uses_NOAA == 1, 'yes', 'no'),
         uses_AT = str_detect(NOAA_var, 'air_temperature')) |>
  ggplot(aes(x=mean_crps, y = manuscript_name, fill = model_type)) +    # Different pattern for each group
  geom_bar_pattern(aes(pattern = as.factor(uses_AT)),
                   stat = "identity",
                   alpha = 0.8,
                   pattern_fill = "black",
                   pattern_colour = "black",
                   pattern_spacing = 0.04,
                   pattern_alpha = 1,
                   colour = 'black') +
  scale_y_reordered() +
  labs(y='Model', x = 'Mean relative skill (°C)') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe')) +
  scale_pattern_type_manual(values=c(NA, NA)) +
  theme_bw(base_size = 10) +
  guides(pattern = guide_legend(override.aes = list(fill = "white", pattern_spacing = 0.02),
                                title = 'Uses air temperature\nas a covariate?'),
         fill = guide_legend(override.aes = list(pattern = "none"), title = 'Model class')) +
    theme(legend.box = 'horizontal')

@@

ggpubr::ggarrange(ggarrange(NULL, as_ggplot(get_legend(skill_summary_RW)), NULL, NULL, widths =  c(0.2, 0.9,0.2, 1.1), nrow = 1),
                  ggarrange(skill_summary_RW_nolegend,  NULL, skill_horizon_RW, align = 'h', widths =  c(0.9,0.05, 1.1), nrow = 1), 
                  heights = c(0.5, 1),nrow = 2) |> 
  ggsave(filename = 'Plots/FigureSnew.png', height = 17, width = 18, units = 'cm')

ggsave(skill_horizon_RW, filename = 'Plots/FigureSnew1.png', height = 10, width = 13, units = 'cm')
```

```{r}
null_scores_T <- temperature_scores |>
  mutate(horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) %>% 
  filter(model_id %in% baselines$model_id, 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |> 
  group_by(model_id, horizon) |> 
  summarise(mean_crps = mean(crps, na.rm = T)) %>% 
  mutate(model_id = factor(model_id, levels = c('climatology', 'persistenceRW'), labels = c("day-of-year", "persistence"))) %>% 
  ggplot(aes(x=horizon,y = mean_crps, colour = model_id)) + 
  geom_line() + 
  scale_x_continuous(breaks = seq(2,30, 2)) + 
  theme_bw() + 
  labs(x= 'Horizon (days)', y = 'Mean CRPS (°C)', title = 'Water temperature') + 
  scale_colour_viridis_d(name = 'Null Model', begin = 0.2, end=0.9) +
  theme(panel.grid.minor = element_blank())

null_scores_DO <- oxygen_scores |>
  mutate(horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) %>% 
  filter(model_id %in% baselines$model_id, 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |> 
  group_by(model_id, horizon) |> 
  summarise(mean_crps = mean(crps, na.rm = T)) %>% 
  mutate(model_id = factor(model_id, levels = c('climatology', 'persistenceRW'), labels = c("day-of-year", "persistence"))) %>% 
  ggplot(aes(x=horizon,y = mean_crps, colour = model_id)) + 
  geom_line() + 
  scale_x_continuous(breaks = seq(2,30, 2)) + 
  theme_bw() + 
  labs(x= 'Horizon (days)', y = 'Mean CRPS (mg/L)', title = 'Dissolved oxygen') + 
  scale_colour_viridis_d(name = 'Null Model', begin = 0.2, end=0.9) +
  theme(panel.grid.minor = element_blank())

ggarrange(null_scores_T, null_scores_DO, common.legend = T) %>% 
  ggsave(filename = 'Plots/Figure_Snew2.png', height = 10, width = 18, units = 'cm')
```
